Nested sampling with two objective functions

### 2016-02-18 Paper/ms.tex
An appendix describing how to calculate uccs

%\appendix
%\section{Appendix Title}
%
%Main text.

>>>>

\appendix
\section{Appendix 1: Fast computation of upper corner counts}
The upper corner count of particle $i$ is defined as the value of
$\hat{X}$ at the position of particle $i$. Less formally, it is the number
of other particles that are `up and to the right' of particle $i$ in
a plot like Figure~\ref{fig:joint1}.

\begin{eqnarray}
C_i = \sum_{\substack{j=1\\j \neq i}}^N
\mathds{1}\left[L_1(\xx_j) \geq L_1(\xx_i), L_2(\xx_j) \geq L_2(\xx_i)\right]
\end{eqnarray}
